Exploiting the Social Graph: Increasing Engagement via Collaborative Interactive Evolution

### 2017-01-27 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Changed the title again...
in → via
What do you think, @mariosky?
Got it back to 8 pages
Mainly reducing a bit captions and tables and eliminating one
figure. Check @mariosky I didn't take off anything important.

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

@@

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

@@

\title{Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution}
% Changed it to "Social". What do you think? - JJ
% Great! - M

\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

@@

\begin{abstract}
Interactive evolution is the leading technique employed by 
Evolutionary Art researchers, where users' preferences guide the search. A common
practice is to develop Interactive Evolutionary Computation (IEC) algorithms
as web applications in order to give users easy access to the
application as the algorithms 
often depend on volunteers who visit the system to interactively help with fitness assignement. 
However, there are several drawbacks that limit user participation 
such as human fatigue and boredom resulting from evaluating 
a large number of phenotypes. 
To tackle these issues, in this paper we propose the design of IEC systems using a human-centered 
approach, with a framework consisting of a social network of 
volunteers, interacting with a population consisting also of a network 
of phenotypes. In this work we suggest the use of a graph model as a practical 
and efficient tool for mapping the relationships 
found in the system. A case study is presented as proof-of-concept, 
providing both conceptual and implementation details of a graph based model 
as it is  applied in the implementation of an IEC system. 
As the results show, the data model was successfully applied in a gamification technique 
developed to increase user engagement, which means that this technique can successfully be used to
decrease user fatigue and thus increase {\em computer power}
delivered by the set of users.
\end{abstract}

@@

\item {\bf Has} The relation describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  phenotypes stored
in them.  In figure \ref{fig:has} the {\tt has} relationship 
between certain nodes $user$, $phenotype$ and $collection$ is shown.

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=2.5in]{img/edge_properties_has.png}
    \caption{ The {\tt has} relationship type example and attributes.}
    \label{fig:has}
\end{figure}

@@

\begin{table*}
  \small
  \caption{ URLs used for each deployment.}
  \label{tab:urls} 
  \centering
  \small
  \begin{tabular}{l l  l l l}
    \hline\noalign{\smallskip}
     Deployment & Heroku URL & Shortened URL & Analytics & Github Repository \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    B   & evodrawings01.herokuapp.com & goo.gl/jLis4Q & goo.gl/jLis4Q.info &  \\ \hline
    G   & evodrawings02.herokuapp.com & goo.gl/jqjNy5 & goo.gl/jqjNy5.info &  \\ \hline
    GG  & evodrawings03.herokuapp.com & goo.gl/J8TCe1 & goo.gl/J8TCe1.info &  \\ \hline
    \end{tabular}
\end{table*}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users are ranked by
		the number of phenotypes they rated, in the \emph{x} axis is the rank, and in the \emph{y} axis 
		the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}

>>>>

% *** CITATION PACKAGES ***
%
\usepackage{cite}

@@

@@

\title{Exploiting the Social Graph: Increasing Engagement via
  Collaborative Interactive Evolution}
% Changed again to "via" - JJ

\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391}}

@@

\begin{abstract}
Interactive evolution, where users' preferences guide the search, is
one of the leading techniques employed by Evolutionary Art
researchers. It is normally implemented as a web application to lower
the access threshold since it often depends on volunteers who visit
the system for fitness assignement. However,  several drawbacks limit
user participation: human fatigue and boredom result from evaluating 
a large number of phenotypes. To tackle these issues, in this paper we
propose an IEC system designed using a human-centered approach, with a
framework consisting of a social network of  
volunteers interacting with a population consisting also of a network 
of phenotypes, which also uses a graph model as a practical 
and efficient tool for mapping the relationships between actors and
objects in the system. A case study is presented as proof-of-concept, 
providing both conceptual and implementation details of a graph based model 
as it is  applied in the implementation of an IEC system. Our
experiments show that the data model can be successfully applied in a
gamification technique developed to increase user engagement, which
implies that this technique can successfully be used to 
decrease user fatigue and thus increase {\em performance} of the
interactive system.
\end{abstract}

@@

\item {\bf Has} The relation describes an ownership relation between users and
those collections they own. Also a collection {\tt has}  phenotypes stored
in them.
% In figure \ref{fig:has} the {\tt has} relationship 
% between certain nodes $user$, $phenotype$ and $collection$ is shown.

@@

% \begin{figure}[!t]
%     \centering
%         \includegraphics[width=2.5in]{img/edge_properties_has.png}
%     \caption{ The {\tt has} relationship type example and attributes.}
%     \label{fig:has}
% \end{figure}

@@

\begin{table}
  \small
  \caption{ Deployment data. URLs were {\tt
      evodrawings0(1,2,3).herokuapp.com}. For analytics URLs, add {\tt
    .info}.}
  \label{tab:urls} 
  \centering
  \small
  \begin{tabular}{l l l }
    \hline\noalign{\smallskip}
     Deployment &  Shortened URL &  Github Repository \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    B   & goo.gl/jLis4Q &   \\ \hline
    G   & goo.gl/jqjNy5 &  \\ \hline
    GG  & goo.gl/J8TCe1 &   \\ \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_2.png}
    \caption{User network view of the Base deployment}
    \label{fig:B-network}
\end{figure}
\begin{figure}[!t]
    \centering
        \includegraphics[width=3.5in]{img/user_known_3.png}
    \caption{User network view of the Graph Gamification deployment}
    \label{fig:GG-network}
\end{figure}
\begin{figure*}[!t]
    \centering
        \includegraphics[width=5.5in]{img/comparison.png}
    \caption{Users ranked by the number of phenotypes they rated vs. the number of phenotypes evaluated using a logarithmic scale. } % Explain a little more and label axes. The
                         % three lines have the same label,
                         % "participation". Not too clear - JJ
                         % Done - Mario
    \label{fig:top-ranked-participation}
\end{figure*}
